Git Learning Notes

### 2014-10-28 ch-intro/ch-intro.tex
camera ready

\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{blackbody1}
\caption{Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius}.}
\label{fig:introbb}
\end{figure}

The successful deployment of \gls{ecd} based on \ce{WO3} relies on several factors:\cite{Granqvist2000}
\begin{itemize}
\item low cost transparent conductive materials with low resistivity;
\item low cost ion electrolyte of poor electron mobility;
\item high yield growth method of \ce{WO3} and integration with other manufacturing process;
\item and life cycle $> 10^5$ for long time outdoor usage.
\end{itemize}
The deficiency of \gls{ecd} based on amorphous or polycrystalline \ce{WO3} film is the accumulation of ions at the film surface preventing further intercalation,\cite{Dini1996} which led to low coloration efficiency and short life time. In contrast, nano-structured single crystalline \ce{WO3} could bypass this limitation, as detailed in Sec.~\ref{sec:nanoadv}.

@@

Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the bandgap, then the carriers (electron and hole) drift and generate free radicals, i.e., \ce{OH.}, which enable further reactions. For water splitting using solar energy, the bandgap should be within $2.0 \sim 3.0 $ eV, and \gls{cb} edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the \gls{vb} top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
\begin{subequations}\label{eq:h2o}
\begin{align}
4\ce{h^+} +  \ce{H2O} &\rightarrow \ce{O2} + 4\ce{H^+} \label{eq:hervb}\\
4\ce{H^+} +  4e^- &\rightarrow 2\ce{H2} \label{eq:hercb}
\end{align}
\end{subequations}
As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2} versus \gls{nhe}, and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}. So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone. Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide.
% wo3 vs NHE
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{woxnhe.jpg}
\caption[Band position of \ce{WO3} versus NHE]{Band position of \ce{WO3} in contact with aqueous electrolyte at pH 1. Reproduced from Ref.\cite{Gratzel2001}}
\label{fig:woxnhe}
\end{figure}
Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds\cite{Hepel2001,Luo2001,Watcharenwong2008}. The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}

@@

Specifically/in regarding to the contents of this study, electrochromic applications based on \gls{tmo} nanowires will benefit from the reduced diffusion depth by eliminating the deficiency of ions accumulation accounted in amorphous oxide thin film devices, which, in turn, leads to shorter response time and higher coloration efficiency.\cite{Huang2008a,Scherer2012} And photocatalytic applications using \gls{tmo} nanostructures could harvest the huge surface area on which unsaturated bond reside, thereby enabling a much higher efficiency.\cite{Mills1993,Merki2011,Chen2011b}

>>>>

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{blackbody1}
\caption{Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius}.}
\label{fig:introbb}
\end{figure}

The successful deployment of \gls{ecd} based on \ce{WO3} relies on several factors:\cite{Granqvist2000}
\begin{itemize}
\item low cost transparent conductive materials with low resistivity;
\item low cost ion electrolyte of poor electron mobility;
\item high yield growth method of \ce{WO3} and integration with other manufacturing process; and 
\item life cycle $> 10^5$ for long time outdoor usage.
\end{itemize}
The deficiency of \gls{ecd} based on amorphous or polycrystalline \ce{WO3} film is the accumulation of ions at the film surface preventing further intercalation,\cite{Dini1996} which led to low coloration efficiency and short life time. In contrast, nano-structured single crystalline \ce{WO3} could bypass this limitation, as detailed in Sec.~\ref{sec:nanoadv}.

@@

Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the bandgap, then the carriers (electron and hole) drift and generate free radicals, i.e., \ce{OH.}, which enable further reactions. For water splitting using solar energy, the bandgap should be within $2.0 \sim 3.0 $ eV, and \gls{cb} edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the \gls{vb} top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
\begin{subequations}\label{eq:h2o}
\begin{align}
4\ce{h^+} +  \ce{H2O} &\rightarrow \ce{O2} + 4\ce{H^+} \label{eq:hervb}\\
4\ce{H^+} +  4e^- &\rightarrow 2\ce{H2} \label{eq:hercb}
\end{align}
\end{subequations}
As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2} versus \gls{nhe}, and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}. So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone. Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide.
% wo3 vs NHE
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{woxnhe.jpg}
\caption[Band position of \ce{WO3} versus NHE]{Band position of \ce{WO3} in contact with aqueous electrolyte at pH 1. Reproduced from Ref.\cite{Gratzel2001}}
\label{fig:woxnhe}
\end{figure}
Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds\cite{Hepel2001,Luo2001,Watcharenwong2008}. The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}

@@

In regarding to the contents of this study, electrochromic applications based on \gls{tmo} nanowires will benefit from the reduced diffusion depth by eliminating the deficiency of ions accumulation accounted in amorphous oxide thin film devices, which, in turn, leads to shorter response time and higher coloration efficiency.\cite{Huang2008a,Scherer2012} And photocatalytic applications using \gls{tmo} nanostructures could harvest the huge surface area on which unsaturated bond reside, thereby enabling a much higher efficiency.\cite{Mills1993,Merki2011,Chen2011b}

### 2014-10-28 ch-moox/moox.tex
camera ready

% git version control added 012614
\chapter{Vapor-Solid-Solid Growth of MoO$_3$}

@@

The coordination number of Mo in \ce{MoO3} is six, so usually \ce{MoO6} octahedra are considered as the building blocks. As shown in Fig.~\ref{fig:mo3model}, the layered structure consisting of zig-zag rows of edge-sharing \ce{MoO6} octahedra, while the rows are mutually connected by corners.
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{MoO3_model}
\caption[\ce{MoO3} crystal model]{\ce{MoO3} crystal model.}
\label{fig:mo3model}
\end{figure}
While considering the fact that four of the six surrounding O atom are at distances from 1.67 to 1.95 \AA, while the remaining two are as far as 2.25 and 2.33 \AA, \ce{MoO3} could also be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis. The infinite chains of \ce{MoO4} tetrahedra from half-layers in the $ac$ plane. Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer.\cite{Itoh2001a} This view stresses that the \ce{MoO6} octahedra are rather distorted.
%A brief summary of crystallography, band structure and dielectric function is listed in Appendix.

@@

The growth layout is schematically shown in Fig.~\ref{fig:mooxgrowth}. Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace. To facilitate discussion and provide a tight context, the author define the position of substrate as the coordinate of its upper-stream edge along this temperature axis, i.e., the substrate location is 7 in in Fig.~\ref{fig:mooxgrowth}. The usual length of Si substrate is 1 in. When positioned at 7 in, it is then located in a temperature zone of $650 \sim 350$ \si{\degreeCelsius}.
% cvd layout
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{CVD_and_temp_MoO3.jpg}
\caption[CVD growth setup of \ce{MoO3}]{CVD growth setup of \ce{MoO3}. The triangular labels $\blacktriangledown$ were measured points at ambient environment. The nominal substrates temperature were estimated from interpolation data.}
\label{fig:mooxgrowth}
\end{figure}

@@

\fbox{%
\parbox{0.8\textwidth}{%
A transverse growth mode exists with growth direction perpendicular to the catalyst-deposition interface, promoting \ce{MoO3} nanoplate and nanobelt growth. A axial growth mode akin to conventional VLS process exists, and is responsible for \ce{MoO3} tower-like growth.
}%
}

@@

\gls{fl} materials attracts intensive research efforts recently. This study also made some efforts using liquid exfoliation method to prepare \gls{fl} \ce{MoO3}. The exfoliated \ce{MoO3} was characterized using UV-Vis and TEM. The optical contrast of \gls{fl} \ce{MoO3} on \ce{SiO2}-Si is also calculated, which could serve as a guideline to identify \gls{fl} \ce{MoO3} using optical microscope.

The exfoliation solution is 30\% isopropanol (IPA) in DI water, which has been proved to work well on other layered compounds.\cite{Halim2013} After 20 min sonication, the dispersion appears milky. The transmission spectra of this dispersion immediately upon sonication and after 40 h of gravity sedimentation were measured and compared in Fig.~\ref{fig:moabs}. The t0 line mainly arise from the scattering of flakes in the dispersion. There are two scattering mechanisms: Rayleigh scattering and Tyndall scattering. Rayleigh scattering, which occurs when particles are comparable to wavelength, is inversely proportional to the fourth power of wavelength; while Tyndall scattering, which occurs when the particles are larger, is inversely proportional to the square of the wavelength. To fully evaluate the true absorbance of the sample itself, one needs to decouple the scattering part from apparent absorbance. Generally, one part of spectrum away from absorption edge is selected and assumed it is only caused by scattering. Then an empirical dependence shown in Eq.~\ref{eq:sca2} is used in the polynomial fitting model.

\begin{align}
Abs_{sca}  & = a\times \lambda^{n}  \label{eq:sca1}\\
\log{Abs_{sca}} & = \log{a} + n*\log{\lambda} \label{eq:sca2}
\end{align}

After least-squares fitting, the coefficients $a$ and $n$ can be used to estimated the scattering in other wavelengths. The fitting of $n$ usually falls between -2 and -4. The author examined the t40h line in Fig.~\ref{fig:moabs} and found the scattering part is almost zero. Therefore no scattering fitting was performed.

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moabs}\includegraphics[width=0.45\textwidth]{MoO3-abs}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mobg}\includegraphics[width=0.45\textwidth]{MoO3-bg}}
\caption[UV-Vis spectra of exfoliated \ce{MoO3}]{UV-Vis spectra of exfoliated \ce{MoO3}. (a) UV-Vis absorbance spectra of exfoliated \ce{MoO3}. Dashed line (t0) represents measurement immediately after sonication, and solid line (t40h) is obtained after sitting for 40 h. The dot dashed line is reference spectrum of the 30\% IPA. (b) Band gap estimation}
\label{fig:mouv}
\end{figure}

According to the corrected absorbance spectrum, optical bandgap can be deduced, which is known as Tauc Plot.\cite{Tauc1972} The procedure is recapitulated here briefly. Eq.~\ref{eq:tauc} is given to empirically relate optical band gap to absorption.

\begin{equation}\label{eq:tauc}
 (h\nu \alpha)^{\frac{1}{n}} = B(h\nu - E_g^{opt}),
\end{equation}
where B is a proportional coefficient, $\alpha$ is absorption coefficient\footnote{The absorbance $A = 0.4343\alpha*l$, where l is the optical path} and $E_g^{opt}$ is defined as optical bandgap. The value n is correlated to the nature of optical transition.
\begin{itemize}
\item For direct allowed transition, n = 1/2;
\item For direct forbidden transition, n = 3/2;
\item For indirect allowed transition, n = 2;
\item And for indirect forbidden transition, n = 3.
\end{itemize}

When the transition nature of sample is not well known, one should apply each to check which one provide the best fit. Depending on the synthesis methods and \ce{MoO3} morphologies, the transition phenomena might vary. On the \ce{MoO3} films, \citeauthor{Bouzidi2003} assumed a direct gap (n = 1/2)\cite{Bouzidi2003} while \citeauthor{Szekeres2002} used an indirect gap.\cite{Szekeres2002} The author use n = 2 in this work, plot $\sqrt{(h\nu \alpha)}$ versus photon energy, and extrapolate the linear part onto $h\nu$ axis. The intercept is used as $E_g^{opt}$ then. The estimated energy gap and some results from previous studies is summarized in Table.~\ref{tab:mobg}.

\begin{table}[htb]
\centering
\caption{Optical band gaps of \ce{MoO3}}\label{tab:mobg}
\begin{tabular}{lccr}
\toprule
&\multicolumn{2}{c}{Band gap} \\
\cmidrule(l){2-3}
Reference & value(eV) & orientation & material states\\
\midrule
\cite{Deb1968}   & 2.96  & $E\parallel c_0$ & single crystal\\
\cite{Deb1968}   & 2.80  & $E\perp c_0$ & single crystal \\
\cite{Julien1995} & 2.8$\sim$ 3.2 & NA & films\\
 this work  & 3.1  & NA & nanoflakes\\
\bottomrule
\end{tabular}
\end{table}

An alternative approach is a) define $Y = \alpha E=\alpha h\nu$, and obtain $Y' = \frac{\partial Y}{\partial E}$, then b) plot $Y'/Y$ versus $h\nu$. The band gap value can be obtained from the intercept of extrapolated line on photo energy axis.\cite{Choopun} This approach is not difficult to comprehend as long as we notice from Eq.~\ref{eq:tauc}, $Y = B (h\nu - E_g^{opt})^n$ and $Y' = B n(h\nu - E_g^{opt})^{n-1}$. The advantage is one can also estimate n without using assumption.

The dielectric constants\footnote{Not a constant at all, instead, it has complicated dependence on photon energy} ($\epsilon = \epsilon_1 + i*\epsilon_2$) of \ce{MoO3} have been studied in several reports.\cite{Deb1968,Sabhapathi1995,Miyata1996,Abdellaoui1997,Mondragon1999} The author extracted $\epsilon_1$ from Ref.~\cite{Itoh2001a} due to the wide photon energy range utilized there. Notice that $\epsilon_2$ is approximately zero when $h\nu$ is less than 4 eV. Since this study is primarily concerned with the optical contrast of few-layered \ce{MoO3} in visible wavelength region ($h\nu < 3$ eV), the refractive indices $n$ is calculated from $n = \sqrt{\epsilon_1}$. Due to the orthorhombic phase, \ce{MoO3} exhibit birefringence, that is there are two refractive indices, $n_c$ and $n_a$, as shown in Fig.~\ref{fig:moind}. The refractive index is between $ 2.2\sim 2.4$ along $a$ axis, and $ 2.5\sim 2.8$ along $c$ axis.

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moind}\includegraphics[width=0.45\textwidth]{n_MoO3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mocon}\includegraphics[width=0.45\textwidth]{MoO3_1L}}
\caption[Refractive indices of \ce{MoO3}]{Refractive indices of \ce{MoO3}. (a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis. (b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si. The $x$ axis is \ce{SiO2} thickness, $y$ axis is wavelength. It is assumed that the incident light is polarized along $c$ axis of \ce{MoO3}.}
\label{fig:mofl}
\end{figure}

Fig.~\ref{fig:mocon} illustrates the optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si when the incident light is polarized along $c$ axis of \ce{MoO3}. One can see that there is a pseudo-periodical trend with either wavelength or \ce{SiO2} thickness fixed. The positive extreme occur at around 80 nm and 240 nm \ce{SiO2} layer, slightly less than the optimum for observing graphene. The refractive indices of Si and \ce{SiO2} within visible wavelengths and MATLAB source code for optical contrast calculation is included in Appendix~\ref{app:matlab}, with which one can readily evaluate the few layers \ce{MoO3} scenarios and the circumstance when incident light is polarized along $a$ axis.

The dimension and phase of exfoliated \ce{MoO3} is examined using TEM. Fig.~\ref{fig:motem} shows the size of exfoliated \ce{MoO3} is about 500 nm. High-resolution TEM (HRTEM) image was taken to assess the \ce{MoO3} crystallinity. The clearly resolved lattices indicate high crystal quality of these exfoliated \ce{MoO3}.
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{exf_moo3.jpg}
\caption[TEM images of exfoliated \ce{MoO3}]{TEM images of exfoliated \ce{MoO3}. (a) TEM image and (b) HRTEM image of FL \ce{MoO3} obtained by liquid sonication method.}
\label{fig:motem}
\end{figure}
Nevertheless, identifying these few layer \ce{MoO3} under optical microscope is still difficult due to both the small flake size and low contrast.\footnote{Human eye threshold contrast (contrast sensitivity)$^{-1}$ is about 10\%.} One need to improve the liquid exfoliation process to obtain larger dimension and high yield. This is, however, beyond the scope of current study.

>>>>

% git version control added 012614
\chapter{Vapor-Solid-Solid Growth of MOLYBDENUM OXIDE}

@@

The coordination number of Mo in \ce{MoO3} is six, so usually \ce{MoO6} octahedra are considered as the building blocks. As shown in Fig.~\ref{fig:mo3model}, the layered structure consisting of zig-zag rows of edge-sharing \ce{MoO6} octahedra, while the rows are mutually connected by corners.
\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{MoO3_model}
\caption[\ce{MoO3} crystal model]{\ce{MoO3} crystal model.}
\label{fig:mo3model}
\end{figure}
While considering the fact that four of the six surrounding O atom are at distances from 1.67 to 1.95 \AA, while the remaining two are as far as 2.25 and 2.33 \AA, \ce{MoO3} could also be considered as built up of chains of \ce{MoO4} tetrahedra connected by the sharing of two oxygen corners with two neighbouring tetrahedra in $c$ axis. The infinite chains of \ce{MoO4} tetrahedra from half-layers in the $ac$ plane. Two half-layers, which are stapled along $b$ axis, build up one \ce{MoO3} layer.\cite{Itoh2001a} This view stresses that the \ce{MoO6} octahedra are rather distorted.
%A brief summary of crystallography, band structure and dielectric function is listed in Appendix.

@@

The growth layout is schematically shown in Fig.~\ref{fig:mooxgrowth}. Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace. To facilitate discussion and provide a tight context, the author define the position of substrate as the coordinate of its upper-stream edge along this temperature axis, i.e., the substrate location is 7 in in Fig.~\ref{fig:mooxgrowth}. The usual length of Si substrate is 1 in. When positioned at 7 in, it is then located in a temperature zone of $650 \sim 350$ \si{\degreeCelsius}.
% cvd layout
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{CVD_and_temp_MoO3.jpg}
\caption[CVD growth setup of \ce{MoO3}]{CVD growth setup of \ce{MoO3}. The triangular labels $\blacktriangledown$ were measured points at ambient environment. The nominal substrates temperature were estimated from interpolation data.}
\label{fig:mooxgrowth}
\end{figure}

@@

\emph{
A transverse growth mode exists with growth direction perpendicular to the catalyst-deposition interface, promoting \ce{MoO3} nanoplate and nanobelt growth. A axial growth mode akin to conventional VLS process exists, and is responsible for \ce{MoO3} tower-like growth.
}

@@

%\input{./ch-moox/mooptics}
The optical properties of the as-grown specimen was evaluated using \gls{drs} method. Fig.~\ref{fig:modrs} show the hemisphere diffuse reflection spectrum from 800 nm to 250 nm, where the diffuse reflection kept increasing from 27\% to 33\% when incident wavelength scanned from 800nm to about 400 nm, then drop sharply to 15\% between 400 nm and 300 nm. The KMT function fitting was used to estimated the energy gap, as displayed in Fig.~\ref{fig:mokmt}. Extrapolation indicated a gap of 3.2 eV, corresponding to absorption edge at 387 nm. This matches well with the DRS data.
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:modrs}\includegraphics[width=0.45\textwidth]{moo3_DRS}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mokmt}\includegraphics[width=0.45\textwidth]{moo3_kmt}}
\caption[DRS spectrum of \ce{MoO3} nanostructures]{DRS spectrum of \ce{MoO3} nanostructures: (a) diffuse reflection spectrum, and (b) the associated KMT function.}
\label{fig:moo3drs}
\end{figure}
Another reflection peak was found at 260 nm, illustrating there is more complex electronic band structures above 4 eV. As a comparison, the estimated energy gap and results from previous studies is summarized in Table~\ref{tab:mobg}.
\begin{table}[htb]
\centering
\caption{Optical band gaps of \ce{MoO3}}\label{tab:mobg}
\begin{tabular}{lccr}
\toprule
&\multicolumn{2}{c}{Band gap} \\
\cmidrule(l){2-3}
Reference & value(eV) & orientation & material states\\
\midrule
\cite{Deb1968}   & 2.96  & $E\parallel c_0$ & single crystal\\
\cite{Deb1968}   & 2.80  & $E\perp c_0$ & single crystal \\
\cite{Julien1995} & 2.8$\sim$ 3.2 & NA & films\\
 this work  & 3.2  & NA & nanoflakes\\
\bottomrule
\end{tabular}
\end{table}

### 2014-10-28 ch-tms/tms.tex
camera ready

\chapter{TEM-RAMAN STUDY ON INDIVIDUAL TUNGSTEN OXIDE-TUNGSTEN DISULFIDE CORE-SHELL NANOWIRE}

@@

A comprehensive understanding of the structure-property relation, which is essential to successful application of nanomaterials, is often hindered by the ensemble averaged characterizations in conventional methods. The present work in this chapter, to some extent, circumvents this limitation by leveraging a home-built micromanipulator apparatus to transfer the nanostructures between TEM grids and other desired substrates. And considerable insight on the \ce{WO3}-\ce{WS2} core-shell nanostructures was obtained: few-layer, even single-layer \ce{WS2} nanotube was observed with \ce{WO3} core; layer dependent Raman spectra were studied at on-resonance and off-resonance conditions; the fingerprint of few-layer \ce{WS2} was revealed; photoluminescence from core-shell NWs was identified. These results hold great values to the application of \ce{WO3}-\ce{WS2} heterostrucutres in photocatalysis and photoelectrochemical applications. More important, this technique of TEM-Raman integrated study could be readily applied to a variety of other nanomaterials, therefore opening a broad spectrum for the understanding of the structure-property relation, propelling the potential nano-engineering applications.

@@

>>>>

\chapter{TUNGSTEN OXIDE-TUNGSTEN DISULFIDE NANOWIRES}

@@

A comprehensive understanding of the structure-property relation, which is essential to successful application of nanomaterials, is often hindered by the ensemble averaged characterizations in conventional methods. The present work in this chapter, to some extent, circumvents this limitation by leveraging a home-built micromanipulator apparatus to transfer the nanostructures between TEM grids and other desired substrates. Considerable insight on the \ce{WO3}-\ce{WS2} core-shell nanostructures was obtained: few-layer, even single-layer tubular \ce{WS2} nanostructure was observed with \ce{WO3} core; layer dependent Raman spectra were studied at on-resonance and off-resonance conditions; the fingerprint of few-layer \ce{WS2} was revealed; photoluminescence from core-shell NWs was identified. These results hold great values to the application of \ce{WO3}-\ce{WS2} heterostrucutres in photocatalysis and photoelectrochemical applications. More important, this technique of TEM-Raman integrated study could be readily applied to a variety of other nanomaterials, therefore opening a broad spectrum for the understanding of the structure-property relation, propelling the potential nano-engineering applications.

@@

In summary, synthesis of \ce{WO3} and \ce{MoO3} nanostructures based on CVD method were thoroughly investigated in this study. Sodium impurity effect was revealed and \ce{Na5W14O44} nanowire was first reported. Partially enlightened by this discovery, a new VSS growth mechanism of \ce{MoO3} was found and the growth dynamics was systematically probed. Comprehensive electron microscopy characterizations were performed on both \ce{WO3} and \ce{MoO3}. And the insight of growth kinetics can be used to establish a systematic connection between the interaction of transition metal oxide and alkaline metal ions. Besides, seeded growth of \ce{WO3} was demonstrated to be an effective and scalable approach for obtaining single crystalline 1D \ce{WO3} nanostructure. Based on these \ce{WO3} nanowires, \ce{WO3}-\ce{WS2} heterostructure was synthesized using a simple sulfurization process and single-walled \ce{WS2} tubular core-shell nanowire was observed. More important, a TEM-Raman integrated approach was tested aiming at providing a location-resolved map between crystal structure and optical properties. As a result, layer number dependence of Raman spectra on \ce{WS2} tubular nanostructure was fingerprinted, and direct bandgap \gls{pl} from \ce{WS2} was observed. This result indicates a broad space for band structure tuning of \ce{WO3}-\ce{WS2}. Moreover, the integration of TEM-Raman serves as an excellent tool to correlation the structure-property relationship for nanomaterials.

For future work, the author suggested several following perspectives:
\begin{enumerate}
\item further investigation of \ce{WO3} growth using alkaline metal ions as catalysts;
\item probing the VSS growth method of \ce{MoO3} using HRTEM and analyzing the droplet state; and
\item applying TEM-Raman integrated study onto other nanostructures.
\end{enumerate}

### 2014-10-28 ch-wox/ch-wox.tex
camera ready

\chapter{IMPURITY EFFECTS ON THE GROWTH OF TUNGSTEN OXIDE NANOWIRES}

@@

In a typical ordinary transport experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat and downstream about 2.5 inch the substrate was stationed. The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu$m thermally-grown silicon oxide layer on the polished side. The cleaning procedures have been elucidated on page.~\pageref{ch2sub}. The boat was then loaded into reaction chamber in a way that the powder source was placed in the center of heating zone, and the substrate upstream end was aligned at 6.5 inch.\footnote{As defined in Fig.~\ref{fig:wogrow}} After pumping down, 1 \gls{sccm} \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr. The temperature ramped up to 1000 \si{\degreeCelsius} in 30 min and lasted for 4 h, and subsequently the apparatus was allowed to naturally cool down to room temperature.
% cvd NW growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{CVD_and_temp.jpg}
\caption[\ce{WO3} NW CVD growth]{\ce{WO3} NW CVD growth and the temperature profile. The nominal NWs growth temperature were estimated according to the interpolation data. Zero inch location is defined at the upstream edge of furnace.}
\label{fig:wogrow}
\end{figure}

@@

% W-O bond length
\begin{table}[htb]
\centering
\caption{\ce{W-O} bond length predication}\label{tab:nawobond}
\begin{tabular}{cccc}
\toprule
Fitted center (\si{cm^{-1}}) & length (\AA) & Fitted center (\si{cm^{-1}}) & length (\AA) \\
\midrule
694.6 & 1.900 &  808.6 &  1.821 \\
745.4 & 1.863 &  911.5 &  1.758 \\
764.4 & 1.850 &  933.0 &  1.745 \\
778.7 & 1.840 &   943.5 & 1.740 \\
788.4 & 1.834 &   965.4 & 1.728 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\chapter{IMPURITY EFFECTS ON TUNGSTEN OXIDE NANOWIRES}

@@

In a typical ordinary transport experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat and downstream about 2.5 inch the substrate was stationed. The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu$m thermally-grown silicon oxide layer on the polished side. The cleaning procedures have been elucidated on page~\pageref{ch2sub}. The boat was then loaded into reaction chamber in a way that the powder source was placed in the center of heating zone, and the substrate upstream end was aligned at 6.5 inch.\footnote{As defined in Fig.~\ref{fig:wogrow}} After pumping down, 1 \gls{sccm} \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr. The temperature ramped up to 1000 \si{\degreeCelsius} in 30 min and lasted for 4 h, and subsequently the apparatus was allowed to naturally cool down to room temperature.
% cvd NW growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{CVD_and_temp.jpg}
\caption[\ce{WO3} NW CVD growth]{\ce{WO3} NW CVD growth and the temperature profile. The nominal NWs growth temperature were estimated according to the interpolation data. Zero inch location is defined at the upstream edge of furnace.}
\label{fig:wogrow}
\end{figure}

@@

% W-O bond length
\begin{table}[htb]
\centering
\caption{\ce{W-O} bond length predication}\label{tab:nawobond}
\begin{tabular}{cccc}
\toprule
Fitted center (\si{cm^{-1}}) & length (\AA) & Fitted center (\si{cm^{-1}}) & length (\AA) \\
\midrule
694.6 & 1.900 &  808.6 &  1.821 \\
745.4 & 1.863 &  911.5 &  1.758 \\
764.4 & 1.850 &  933.0 &  1.745 \\
778.7 & 1.840 &   943.5 & 1.740 \\
788.4 & 1.834 &   965.4 & 1.728 \\
\bottomrule
\end{tabular}
\end{table}
For a comprehensive comparison purpose, the Raman fingerprints of various tungsten oxides and tungstate is shown in Table.~\ref{tab:woram2}. 
\begin{table}[htb]
\centering
\caption{Raman fingerprints of tungsten oxides and sodium tungsten compounds}\label{tab:woram2}
\begin{tabular}{lp{3in}r}
\toprule
Phase & Raman Shift (\si{cm^{-1}}) &  Reference   \\
\midrule
\ce{WO2}  & 287(s), 334(w), 514(m), 600(w), 621(w), 785(vs) & \cite{Ma2005} \\
\ce{W18O49}  & broad bands from 750 to 780 & \cite{Guo2012} \\
             &  267(s), 778(s), 969(m) & \cite{Liu2013d} \\
m-\ce{WO3}  & 131(m), 265(m), 327(m), 715(s), 807(vs) &  \cite{Salje1975a,Daniel1987} \\
h-\ce{WO3}  & 162(m), 253(m), 320(m), 645, 690(s), 817(vs) &  \cite{Daniel1987}\\
\ce{WO3.H2O}  & 230(m), 377(w), 428(w), 650(s), 816(vs), 946(vs) &  \cite{Daniel1987} \\
\ce{WO3.2H2O}  & 235, 268(m), 380(w), 662(s), 685(vs), 960(vs) & \cite{Daniel1987} \\
\ce{Na2WO4}  & 94(w), 314(vw), 377(m), 813(m), 930(vs) &  \cite{Lima2011} \\
\ce{Na2W2O7}  & 381(w), 422(w), 763(w), 835(s), 886(m), 948(m), 957(vs) &  \cite{Knee1979} \\
\ce{Na2W4O13} & 263(w), 272(w), 311(w), 366(w), 777(vs), 794(s), 949(m) &\cite{Fomichev1992}\\
\ce{Na5W14O44} & 107(s),695(m), 765(vs), 913(w), 943(m), 965(m)& this work\\
\bottomrule
\end{tabular}

Materials in solid state, 
vw-very weak; w-weak; m-medium; s-strong; vs-very strong
\end{table}
